\documentclass[14pt]{article}
\usepackage[left=2cm, right=2cm, top=2cm]{geometry}
\usepackage{amsmath}
\usepackage{enumitem}
\usepackage{tabto}
\begin{document}

%\hspace{10cm}\text{Name:________________________}
%\textbf{Name :                        }\hspace*{12cm}
%\textbf{Roll No :                        }\\
\begin{center}
\large{\textbf{Government College of Engineering Kannur\\}}
\large{\textbf{Department of Computer Science and Engineering\\}}
\large{\textbf{CSD334: Mini-Project\\}}
\end{center}

\begin{center}
\small{\textbf{\underline{ Project Proposal}\\}}
\end{center}

\begin{table}[ht!]
\begin{center}
\begin{tabular}{|cccc|}
\hline
\multicolumn{4}{|c|}{\textbf{Proposal Prepared By}}                        \\ \hline
\multicolumn{1}{|c|}{Sl No.} & \multicolumn{1}{c|}{KTU Reg No.} & \multicolumn{1}{c|}{Name of Student}              & Signature of Student \\ \hline
\multicolumn{1}{|c|}{1}      & \multicolumn{1}{c|}{KNR22CS008}   & \multicolumn{1}{c|}{Amarnath Panneri} &           \\ \hline
\multicolumn{1}{|c|}{2} & \multicolumn{1}{c|}{KNR22CS043} & \multicolumn{1}{c|}{Muhammed Hanoon Zameel} &  \\ \hline
\multicolumn{1}{|c|}{3} & \multicolumn{1}{c|}{KNR22CS062} & \multicolumn{1}{c|}{Swalih T} &  \\ \hline
\multicolumn{1}{|c|}{4} & \multicolumn{1}{c|}{KNR22CS065} & \multicolumn{1}{c|}{Tom Sebastain} &  \\ \hline
\end{tabular}
\end{center}
\end{table}


\begin{enumerate}
\item Project Title : \textbf{Lab Exam Management System}
\item Problem Statement \\
\tabto{.5cm}Current lab exam systems are inefficient and lack functionality tailored to programming assessments. Teachers face challenges in creating and managing exams for specific groups, while students struggle with inconsistent tools for writing and testing code.
The absence of a centralized platform complicates processes like code evaluation, test case validation, and reporting. Limited feedback mechanisms and manual report generation hinder efficiency and fairness.

A dedicated lab exam management system is needed to enable teachers to create online programming exams, provide students with an integrated code editor for writing and testing, evaluate submissions based on test case correctness, and use AI for partial evaluation. It should also streamline report generation, ensuring accurate and efficient assessments.\\

\item Solution approach \\
\tabto{.5cm}Our proposed exam evaluation system will streamline the examination process, from creation to evaluation, ensuring accuracy and security. Below are the key features and functionalities.
\begin{enumerate}
\item \textbf{User Registration and Authentication}
\begin{itemize}
\item Users can join as a student or teacher by creating accounts or logging in using existing credentials.
\item Authentication ensures secure access to the system.
\end{itemize}
\item \textbf{Room Creation and Exam Setting}
\begin{itemize}
\item Examiners can create exam rooms and upload question papers.
\item Features include specifying exam dates and durations.
\end{itemize}
\item \textbf{Platform-Independent compiler and Proctored UI}
\begin{itemize}
\item The system includes a platform-independent compiler interface for seamless access on any device.
\item A proctored UI prevents students from copying or switching tabs during the examination.
\end{itemize}
\item \textbf{AI Partial Output Detection}
\begin{itemize}
\item An AI-powered module evaluates student's code for partial correctness.
\item This ensures fair grading even if the solution is incomplete but correct to some extent.
\end{itemize}
\item \textbf{Student-Wise Report Generation}
\begin{itemize}
\item The system generates detailed results for each student.
\item Results can be downloaded in PDF format for easy sharing and record-keeping.
\end{itemize}
\item \textbf{Centralized Database}
\begin{itemize}
\item A centralized database stores information about exams, subjects, dates, and student reports.
\item MySQL or a similar relational database management system (RDBMS) is used for efficient data management.
\end{itemize}
\item \textbf{User Notifications}
\begin{itemize}
\item Automated notifications inform students about exam schedules and results.
\item Alerts are sent via email or SMS for timely updates.
\end{itemize}
\end{enumerate}


\item Does any other solution already exist for the stated problem? If yes, give details.
\begin{itemize}
\item Yes, there are existing solutions for exam evaluation, but they often suffer from various limitations.
\begin{enumerate}
\item Manually Conducted Exams
\begin{itemize}
\item {Limitations}
\begin{itemize}
\item Time-Consuming: Teachers must manually check each system for output verification, which is inefficient.  
\item No Proper Partial Output Verification: Results are assessed as correct or incorrect, without acknowledging partial correctness.  
\item System Variability: Each system may behave differently due to inconsistent configurations, causing discrepancies in output.  
\end{itemize}
\end{itemize}
\item Online Exam Platforms
\begin{itemize}
\item HackerRank
\item {Limitations}
\begin{itemize}
\item No Partial Output Detection: Unable to evaluate partially correct solutions, which is essential for fair assessment in coding exams.  
\item Not Best for College Lab Exams: The platform is better suited for corporate hiring assessments than for educational settings.  
\item Limited Offline Support: Requires constant internet connectivity, which can be a challenge for some labs.  
\end{itemize}
\item HackerEarth
\item {Limitations}
\begin{itemize}
\item High Cost: Not affordable for all educational institutions.  
\item Complex Setup: Requires significant technical expertise for exam creation and management.  
\end{itemize}
\item Other Online Platforms
\item {Limitations}
\begin{itemize}
\item Lack of AI Features: Many do not offer advanced features like AI-based partial output evaluation.  
\item Limited Customization: Few platforms allow fully tailored exams to suit specific academic needs.  
\item Proctoring Gaps: Some platforms have limited proctoring features, increasing the risk of cheating.  
\end{itemize}
\end{itemize}
\end{enumerate}
\item A centralized, AI-powered exam evaluation system with robust proctoring, partial output detection, and seamless integration for college labs can effectively address these limitations.
\end{itemize}


\item In what way is your proposed solution better than the existing solution(s)?\\
\tabto{.5cm}Our proposed solution for online examination management offers several advantages over existing methods.
\begin{enumerate}
\item \textbf{Advanced Anti-Cheating Techniques}
\begin{itemize}
\item Most platforms, including ETLab, focus on online proctoring or basic monitoring methods, which can often be bypassed.
\item Our proposed application incorporates robust anti-cheating measures such as tab-locking technology, real-time notifications for unauthorized activity, and automatic banning for rule violations, ensuring a secure and fair examination environment, even in offline settings.
\end{itemize}

\item \textbf{Centralized Timing Mechanism}
\begin{itemize}
\item The application utilizes a centralized API to synchronize the start time for all participants.
\item This ensures a uniform experience and eliminates timing-related issues.
\end{itemize}

\item \textbf{Comprehensive Result Table Generation}
\begin{itemize}
\item The application automatically generates a detailed PDF report with comprehensive analytics, including individual and group performance metrics.
\item Faculty can quickly assess outcomes without manual intervention.
\end{itemize}

\item \textbf{AI-Driven Feedback for Students}
\begin{itemize}
\item Other platforms lack personalized insights into students' weak areas and improvement strategies.
\item Our application uses AI to analyze performance and provide targeted suggestions for improvement, empowering students with actionable insights for skill enhancement.
\end{itemize}

\item \textbf{Uniform Coding Environment}
\begin{itemize}
\item Other platforms may allow students to use their preferred compilers, which can lead to inconsistencies in results.
\item Our application ensures all students use the same compiler, maintaining uniformity in coding environments and evaluation.
\end{itemize}

\item \textbf{Post-Exam Solution Access}
\begin{itemize}
\item Facilitates faculty to upload correct answers.
\item Students can review and self-evaluate their performance after the exam.
\end{itemize}
\end{enumerate}

\item List out the stakeholders of the proposed project.
\begin{enumerate}
    \item \textbf{Users}
    \begin{itemize}
        \item \textbf{Students:}
        \begin{itemize}
            \item Primary users who participate in lab or coding exams.
            \item Access the platform to view exam schedules, take exams, submit solutions, and view results.
            \item Provide feedback on the exam process to improve the platform.
        \end{itemize}
        \item \textbf{Instructors:}
        \begin{itemize}
            \item Use the platform to create, assign, and grade exams.
            \item Provide feedback or comments on student submissions.
        \end{itemize}
    \end{itemize}

    \item \textbf{Administrators}
    \begin{itemize}
        \item \textbf{Platform Managers:}
        \begin{itemize}
            \item Oversee the overall functioning of the platform.
            \item Ensure exams are conducted without technical issues.
            \item Manage user accounts, permissions, and system configurations.
        \end{itemize}
        \item \textbf{Technical Support Staff:}
        \begin{itemize}
            \item Provide assistance to users facing technical difficulties.
            \item Maintain the platform’s performance, security, and reliability.
        \end{itemize}
    \end{itemize}

    \item \textbf{Community/Institution}
    \begin{itemize}
        \item \textbf{Educational Institutions:}
        \begin{itemize}
            \item Deploy the platform for conducting lab and coding exams.
            \item Provide necessary infrastructure, such as servers, internet connectivity, and devices.
            \item Monitor the overall success of the platform and its impact on the exam process.
        \end{itemize}
        \item \textbf{Accreditation Bodies:}
        \begin{itemize}
            \item May review the platform’s features to ensure it meets academic standards.
            \item Provide endorsements or certifications for the system.
        \end{itemize}
    \end{itemize}
\end{enumerate}
\item What will be the impact of this project work on society directly or indirectly?\\
\tabto{.5cm}The impact of a lost and found website on society can be significant, both directly
and indirectly.
\begin{enumerate}
\item \textbf{Direct Impacts}
\begin{itemize}
\item \textbf{Enhanced Examination Integrity} : Anti-cheating features like tab restrictions and notifications ensure a fair evaluation process.
\item \textbf{Improved Efficiency for Faculty} : Automatic evaluation and report generation save time and effort for faculties, enabling them to focus on teaching and curriculum improvement.
\item \textbf{Uniform Experience} : A centralized API ensures synchronized exam start times, regardless of device or location, creating a standardized experience for all students.
\item \textbf{Personalized Feedback for Students} : AI-driven suggestions provide targeted improvement tips, enabling students to focus on weak areas.
\item \textbf{Scalable Solution} : The application can be deployed across diverse environments, such as computer labs and mobile classrooms, making it adaptable to various institutions.
\item \textbf{Accessible Results and Analytics} : Faculty and students have access to detailed performance analytics, which can be used for curriculum adjustments and self-evaluation.
\end{itemize}   
\item \textbf{Indirect Impacts}
\begin{itemize}
\item \textbf{Reduced Administrative Load} : Faculties spend less time on administrative tasks, allowing them to engage in more strategic activities like curriculum development.
\item \textbf{Improved Student Performance} : Immediate feedback and detailed solutions help students learn from mistakes, potentially boosting overall academic performance.
\item \textbf{Enhanced Digital Literacy} : Regular exposure to coding exams and digital tools enhances students' technical proficiency and readiness for real-world scenarios.
\item \textbf{Increased Trust in the Examination Process} : Transparent evaluation and anti-cheating measures build trust among students, faculty, and institutions.
\item \textbf{Encouragement of Ethical Practices} : Discouraging cheating fosters a culture of honesty and accountability in academic settings.
\item \textbf{Institutional Reputation Boost} : Institutions adopting such innovative solutions may gain a competitive edge and improve their reputation among stakeholders.
\item \textbf{Data-Driven Decisions} : Analytics from the application can guide decision-making for curriculum adjustments, identifying trends in student performance and challenges.
\item \textbf{Environmental Impact} : Transitioning to digital examinations reduces the need for paper-based exams, contributing to sustainability.
\end{itemize}
\end{enumerate}
    
\item What technologies do you plan to use for the front-end and back-end?
\begin{enumerate}
\item \textbf{Front-end (Client-side)} :
\begin{itemize}
\item \textbf{React.js} : A JavaScript library for building user interfaces, enabling the creation of reusable UI components and efficient state management.
\item \textbf{Redux.js} : A predictable state container for JavaScript apps, used for managing the application’s state across components seamlessly.
\item \textbf{Vite} : A modern frontend build tool providing fast development and optimized production builds.
\end{itemize}
\item \textbf{Back-end (Server-side)} :
\begin{itemize}
\item \textbf{Node.js} : A JavaScript runtime environment for executing server-side code, featuring an event-driven architecture that supports high-performance, scalable server applications.
 JavaScript code on the server-side. It provides an event-driven architecture that is well-suited for building scalable and high-performance server applications.
\item \textbf{Express.js} : A minimal and flexible web application framework for Node.js, offering powerful features for web server development, routing, and middleware integration.
\item \textbf{Socket.io} : A library for enabling real-time, bidirectional, and event-based communication between the client and server. 
\end{itemize}
\item \textbf{Database} :
\begin{itemize}
\item \textbf{PostgreSQL} :  A robust, open-source relational database known for its reliability, scalability, and support for complex queries.
\tabto{.5cm} Altogether, we utilize the PERN stack for development, integrating modern JavaScript-based technologies for a cohesive and efficient development experience.
\end{enumerate}   

\end{enumerate}
\begin{table}[ht!]
\begin{center}
\begin{tabular}{|cll|}
\hline
\multicolumn{3}{|c|}{\textbf{Proposal Approved By}}                                                                   \\ \hline
\multicolumn{1}{|c|}{Name of Guide} & \multicolumn{1}{c|}{Signature of Guide} & \multicolumn{1}{c|}{Date of Approval} \\ \hline
\multicolumn{1}{|l|}{Dr. Nidheesh N}              & \multicolumn{1}{l|}{}                   &                                       \\ \hline
\end{tabular}
\end{center}
\end{table}
\end{document}

